---
title: "Aaron M8 Class Workspace Project"
author: "Aaron"
date: "7/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
library(tidyverse)
Pets <- read_csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv?complaint_type=Illegal+Animal+Kept+as+Pet&borough=QUEENS")
Pets
Sanitation <- read.csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv?agency_name=Department+of+Sanitation&borough=QUEENS")
```

## NYC Pet and Sanitation 

Through this document I will be comparing the data from NYC regarding illegal animals being kept as pets and requests that belong to the Sanitation Department. For more details on these data sets see <https://data.cityofnewyork.us/resource/erm2-nwe9.csv?complaint_type=Illegal+Animal+Kept+as+Pet&borough=QUEENS> and <https://data.cityofnewyork.us/resource/erm2-nwe9.csv?agency_name=Department+of+Sanitation&borough=QUEENS>.

Below I have taken the data set containing the illegal animals that are being kept as pets in Queens, and I joined it with the set regarding the requests for the Sanitation department in order to group the complaints by address. 

```{r cars}
Pet_NY <- Pets %>%
  left_join(Sanitation,by="incident_address")%>%
  count(Pets, "incident_address",sort = TRUE)
Pet_NY %>%
  select(incident_address)%>%
  count(incident_address)
```
Above, we have created a new table which uses the Pets data set and matches its information with the Sanitation set. We use "Left_join" in order to keep the data from the Pet set and "by" to keep the observations in Pet but compare with a specific observation in Sanitation, "incident_address". 

We do this to have a column that has the address, and a column that has the number of illegal animals kept as pet complaints for that address.

```{r pressure, echo=FALSE}
Sani_NY <- Sanitation %>%
  left_join(Pets,by="incident_address")%>%
  count(Sanitation,"incident_address",sort = TRUE)
Sani_NY%>%
  select(incident_address)%>%
  count(incident_address)
```

Here, we have created a new table which uses the Sanitation data set and matches its information with the Pets set. We use "Left_join" again in order to keep the data from the Sanitation set and "by" to keep the observations in Sanitation but compare with a specific observation in Pets, "incident_address". 

Again, we do this to have a column that has an address, and a column that has the number of sanitation requests for that address.

```{r}
full_join(Pet_NY,Sani_NY,by="incident_address")
```

With this new data set above, we used "full_join" in order to compare the two tables we have created and joining their observations by the "incident address" column. This would make it so that we have a table which contains only the addresses that have complaints in both sets. 
