---
title: "Aaron M8 Class Workspace Project"
author: "Aaron"
date: "7/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
library(tidyverse)
Pets <- read_csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv?complaint_type=Illegal+Animal+Kept+as+Pet&borough=QUEENS")
Pets
Sanitation <- read.csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv?agency_name=Department+of+Sanitation&borough=QUEENS")
```

## NYC Pet and Sanitation 

Through this document I will be comparing the data from NYC regarding illegal animals being kept as pets and requests that belong to the Sanitation Department. For more details on these data sets see <https://data.cityofnewyork.us/resource/erm2-nwe9.csv?complaint_type=Illegal+Animal+Kept+as+Pet&borough=QUEENS> and <https://data.cityofnewyork.us/resource/erm2-nwe9.csv?agency_name=Department+of+Sanitation&borough=QUEENS>.

Below I have taken the data set containing the illegal animals that are being kept as pets in Queens, and I joined it with the set regarding the requests for the Sanitation department in order to group the complaints by address. 

```{r cars}
Pet_NY <- Pets %>%
  left_join(Sanitation,by="incident_address")%>%
  count(Pets, "incident_address",sort = TRUE)
Pet_NY
```



```{r pressure, echo=FALSE}
Sani_NY <- Sanitation %>%
  left_join(Pets,by="incident_address")%>%
  count(Sanitation, "incident_address")
Sani_NY
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
full_join(Pet_NY,Sani_NY,by="incident_address")
```

